### 2020-07-28 paper.tex
initial commit

\documentclass{article}

%other packages
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{physics}

\usepackage[
	style=phys, articletitle=false, biblabel=brackets, chaptertitle=false, pageranges=false, url=true
]{biblatex}

\usepackage{graphicx}

% \usepackage{siunitx}

%\pagestyle{headings}

\title{Paper}
\author{Deepak Mallubhotla}
% want empty date
\date{\today}

\addbibresource{./bibliography.bib}

\graphicspath{{./figures/}}

\begin{document}

\maketitle

\section{Introduction \label{sec:intro}}

\printbibliography

\end{document}

### 2020-07-28 paper.tex
Adding todo items

@@
 \usepackage{amssymb}
-% \usepackage{physics}
+\usepackage{physics}
 
@@
 \usepackage{graphicx}
+\usepackage{todonotes}
+\usepackage{siunitx}
 
-% \usepackage{siunitx}
-
-%\pagestyle{headings}
-
-\title{Paper}
-\author{Deepak Mallubhotla}
-% want empty date
-\date{\today}
+\title{Title}
 
@@
 \section{Introduction \label{sec:intro}}
+\begin{itemize}
+	\item Motivate with~\cite{Tenberg2019} and~\cite{Kolkowitz2015}
+	\item Existing work with Lindhard expression~\cite{QubitRelax}
+	\item Variety of existing superconducting dielectric functions like in~\cite{AGD, llv9, Zimmermann1991, Mattis, Tinkham}.
+	Advantage of Nam expression\cite{Nam1967} is that it's got the worked out dependence on momentum and impurities, both of which we need.
+\end{itemize}
+\section{Methods \label{sec:methods}}
+
+\begin{itemize}
+	\item Include Nam expressions from~\cite{Nam1967}, including the choice for particle density function etc.
+	\item Are there any interesting plots for Nam dielectric function?
+	We're not adding anything to them, so only interesting thing is showing effect of frequency / temperature to show that Nam did indeed describe something that looks like a superconductor.
+	\item Potentially include Lindhard expressions for completeness? or does it suffice to mention them.
+	\item Include noise expressions from~\cite{QubitRelax} and~\cite{Henkel1999}.
+	\item Include the Ford and Weber expressions in~\cite{Ford1984}, for reflection coefficients/ surface impedances.
+	\item Include 3D plot of noise vs $\omega$ and $T$ with presence of the phase transition to superconducting state?
+	\item Include sample plot of noise vs distance here to show overall shape of noise (e.g. show levelling off for $z \rightarrow 0$ and cubic dependence further away, as expected?).
+\end{itemize}
+
+\section{Numerical Techniques \label{sec:technical}}
+
+\begin{itemize}
+	\item Limitations on superconducting dielectric function.
+	In every expression that's worked out for arbitrary momentum, the large-momentum dependence goes as $\frac{1}{k}$, which is clearly unphysical.
+	Issue exists in~\cite{Nam1967, AGD, Tinkham}, etc.
+	\item Include description of cutoff process.
+	\item Include description of the interpolation process.
+	\item Is the numerics of picking the relevant unit scales / discussion of convergence interesting?
+	It might be too obvious that the convergence is expected because these are real quantities.
+	\item Any other potentially interesting approximations?
+	Some integrals have regions entirely discarded because they are too small to matter, which is why the expressions in the Mathematica package are much simpler than what's in Nam.
+\end{itemize}
+
+\section{Experiments \label{sec:experiments}}
+\begin{itemize}
+	\item Show that expression is of right order of magnitude to describe~\cite{Tenberg2019}.
+	\item Look at temperature at which~\cite{Tenberg2019} should show SC effects (not far off!)
+	\item Compare to~\cite{Kolkowitz2015}?
+	Much further from relevant temperature range.
+	\item Metal choices?
+	Obviously large $T_c$ is most important to get noise reduction benefits.
+	What else is most relevant for usable metals?
+\end{itemize}
+\section{Conclusions \label{sec:conclusions}}
 

### 2020-08-04 paper.tex
Adds Nam dielectric function description
Tightens verb choice
Fixes whitespace.
Adds missing coherence factor
Adds noise and reflection coefficient expressions.

@@
 
+\newcommand{\vf}{v_{\mathrm{F}}}
+
 \begin{document}
@@
 
+	The relaxation rate for an electric qubit with dipole moment $\vec{d}$ a distance $r$ from a half space, described in~\cite{Henkel1999} and~\cite{QubitRelax}, can be written
+	\begin{equation}
+		\frac{1}{T_1} = \frac{d^2}{\hbar \epsilon_0} \frac{\omega^3}{c^3} \chi_{i}^{E}(r, \omega) \coth\frac{\omega}{2 T}.
+	\end{equation}
+	For a qubit pointing perpendicular to the surface of the half space,
+	\begin{align}
+		\chi_\perp^E(z, \omega) &= \Re \int_0^{+\infty} \dd{u} \frac{u^3}{v} e^{2 i z v} r_p(u).
+	\end{align}
+	Here, $z$ is measured in units of the vacuum wavelength $\frac{c}{\omega}$, $v = \sqrt{1 - u^2}$ and we take the root $v = i \sqrt{u^2 - 1}$ for $u \geq 1$.
+
+	The reflection coefficients are described by Ford and Weber~\cite{Ford1984}:
+	\begin{align}
+		r_p(u) &= \frac{\epsilon(u) v - \sqrt{\epsilon(u) - u^2}}{\epsilon(u) v + \sqrt{\epsilon(u) - u^2}} \\
+		r_s(u) &= \frac{v - \sqrt{\epsilon(u) - u^2}}{v + \sqrt{\epsilon(u) - u^2}}.
+	\end{align}
+
+	Nam~\cite{Nam1967} describes the electrodynamics for a broad class of superconducting behaviour.
+	Assuming no magnetic impurities and weak coupling, we have
+	\begin{equation}
+		\epsilon(q = u \frac{\omega}{c}, \omega) = 1 + \frac{3 \pi}{\omega^2} \frac{n e^2}{m} \left[\int_{\Delta - \omega}^{\Delta}\dd{\omega'} \tanh(\frac{\omega + \omega'}{2 T}) I_1 + \int_{\Delta}^{\infty} \dd{\omega'} \left( \tanh(\frac{\omega + \omega'}{2 T}) I_1  - \tanh(\frac{\omega'}{2 T})I_2 \right) \right],
+	\end{equation}
+	with
+	\begin{align}
+		I_1 &= F(q, \Re[\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g + 1) \nonumber\\
+		&\quad + F(q, \Re[-\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g - 1) \\
+		I_2 &= F(q, \Re[\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g + 1) \nonumber\\
+		&\quad + F(q, \Re[\sqrt{(\omega +  \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}]) (g - 1) \\
+		F(q, E) &= \frac{1}{q \vf} \left[2 S(E) + (1 - S(E)^2)\ln(\frac{S(E) + 1}{S(E) - 1})\right]  \\
+		S(q, E) &= \frac{1}{q \vf} \left( E - i \left(\Im[\sqrt{(\omega + \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}] + \frac{2}{\tau} \right) \right) \\
+		g &= \frac{\omega' \left(\omega + \omega'\right) + \Delta^2}{\sqrt{\omega'^2 - \Delta^2}\sqrt{(\omega + \omega')^2 - \Delta^2}}.
+	\end{align}
+
 \begin{itemize}
-	\item Include Nam expressions from~\cite{Nam1967}, including the choice for particle density function etc.
+
 	\item Are there any interesting plots for Nam dielectric function?

### 2020-08-06 paper.tex
Removes items from todolist.
Adds text on noise and nam expression, creates general results section

@@
 	\begin{align}
-		\chi_\perp^E(z, \omega) &= \Re \int_0^{+\infty} \dd{u} \frac{u^3}{v} e^{2 i z v} r_p(u).
+		\chi_\perp^E(z, \omega) &= \Re \int_0^{+\infty} \dd{u} \frac{u^3}{v} e^{2 i z v} r_p(u). \label{eq:chi}
 	\end{align}
@@
 	\begin{align}
-		r_p(u) &= \frac{\epsilon(u) v - \sqrt{\epsilon(u) - u^2}}{\epsilon(u) v + \sqrt{\epsilon(u) - u^2}} \\
-		r_s(u) &= \frac{v - \sqrt{\epsilon(u) - u^2}}{v + \sqrt{\epsilon(u) - u^2}}.
+		r_p(u) &= \frac{\pi v - \zeta_p(u)}{\pi v + \zeta_p(u)} \\
+		r_s(u) &= \frac{\zeta_s(u) - \frac{\pi}{v}}{\zeta_s(u) + \frac{\pi}{v}} \\
+		\zeta_p(u) &= 2i \int_0^\infty \dd{y} \frac{1}{\kappa^2} \left( \frac{y^2}{\epsilon(\frac{\omega}{c}\kappa, \omega) - \kappa^2} + \frac{u^2}{\epsilon_(\frac{\omega}{c}\kappa, \omega)} \right) \label{eq:zp} \\
+		\zeta_s(u) &= 2i \int_0^\infty \dd{y} \frac{1}{\epsilon(\frac{\omega}{c}\kappa, \omega) - \kappa^2} \label{eq:zs} \\
+		\kappa^2 &= u^2 + y^2
 	\end{align}
+	As noted in~\cite{QubitRelax}, these expressions remain valid even for nonlocal descriptions of the dielectric constant.
 
-	Nam~\cite{Nam1967} describes the electrodynamics for a broad class of superconducting behaviour.
-	Assuming no magnetic impurities and weak coupling, we have
+	Nam~\cite{Nam1967} describes the electrodynamics for superconductors applicable for clean and dirty materials.
+	Assuming no magnetic impurities and weak coupling, his expressions reduce to
 	\begin{equation}
-		\epsilon(q = u \frac{\omega}{c}, \omega) = 1 + \frac{3 \pi}{\omega^2} \frac{n e^2}{m} \left[\int_{\Delta - \omega}^{\Delta}\dd{\omega'} \tanh(\frac{\omega + \omega'}{2 T}) I_1 + \int_{\Delta}^{\infty} \dd{\omega'} \left( \tanh(\frac{\omega + \omega'}{2 T}) I_1  - \tanh(\frac{\omega'}{2 T})I_2 \right) \right],
+		\epsilon(q, \omega) = 1 + \frac{3 \pi}{\omega^2} \frac{n e^2}{m} \left[\int_{\Delta - \omega}^{\Delta}\dd{\omega'} \tanh(\frac{\omega + \omega'}{2 T}) I_1 + \int_{\Delta}^{\infty} \dd{\omega'} \left( \tanh(\frac{\omega + \omega'}{2 T}) I_1  - \tanh(\frac{\omega'}{2 T})I_2 \right) \right],
 	\end{equation}
@@
 
+\section{General Results}
+
 \begin{itemize}
-
-	\item Are there any interesting plots for Nam dielectric function?
-	We're not adding anything to them, so only interesting thing is showing effect of frequency / temperature to show that Nam did indeed describe something that looks like a superconductor.
-	\item Potentially include Lindhard expressions for completeness? or does it suffice to mention them.
-	\item Include noise expressions from~\cite{QubitRelax} and~\cite{Henkel1999}.
-	\item Include the Ford and Weber expressions in~\cite{Ford1984}, for reflection coefficients/ surface impedances.
 	\item Include 3D plot of noise vs $\omega$ and $T$ with presence of the phase transition to superconducting state?
@@
 
+	Nam's expressions are no longer valid for $k \geq k_\mathrm{F}$, and as $k \rightarrow \infty$ exhibit an unphysical $\flatfrac{1}{k}$ dependence.
+	In order to use~\eqref{eq:zp} and~\eqref{eq:zs}
 \begin{itemize}

### 2020-08-06 paper.tex
adds more text

@@
 
-\section{General Results}
-
-\begin{itemize}
-	\item Include 3D plot of noise vs $\omega$ and $T$ with presence of the phase transition to superconducting state?
-	\item Include sample plot of noise vs distance here to show overall shape of noise (e.g. show levelling off for $z \rightarrow 0$ and cubic dependence further away, as expected?).
-\end{itemize}
+	As seen in figure\todo{Insert 3D plot here}, the temperature dependence for the superconducting state is richer than for the normal state described in~\cite{QubitRelax}.
+	When $\omega$ and $T$ are both much smaller than $T_c$, the figure reveals the expected reduction in noise.
+	As $T \rightarrow T_c$, a smaller $\omega$ is required to facilitate Johnson noise.
+	In figure\todo{Insert chi vs T plot, for Lindhard and Nam}, the more sensitive temperature dependence of the superconductor is visible against a normal state calculation done with the Lindhard function, as in~\cite{QubitRelax}.
+	For $T \rightarrow T_c$, the superconducting state noise approaches that of the normal state, as expected.
 

### 2020-08-06 paper.tex
Adds todos

@@
 
-	The relaxation rate for an electric qubit with dipole moment $\vec{d}$ a distance $r$ from a half space, described in~\cite{Henkel1999} and~\cite{QubitRelax}, can be written
+	The relaxation rate for an electric qubit with dipole moment $\vec{d}$ a distance $r$ from a half space, described in~\cite{Henkel1999} and~\cite{QubitRelax}, can be written\todo{Add description here of how and why (e.g.
+Fermi's golden rule + FD theorem)}
 	\begin{equation}
@@
 
-	The reflection coefficients are described by Ford and Weber~\cite{Ford1984}:
+	The reflection coefficients are described by Ford and Weber~\cite{Ford1984}\todo{Add description of conditions and derivation methods, surface impedance are in quasistatic limit}:
 	\begin{align}

### 2020-08-06 paper.tex
Add todo about Nam

@@
 
-	Nam~\cite{Nam1967} describes the electrodynamics for superconductors applicable for clean and dirty materials.
+	Nam~\cite{Nam1967} describes the electrodynamics for superconductors applicable for clean and dirty materials.\todo{Describe his derivations here, based on Green's function methods \& can generalise to strong-coupling and magnetic impurities}
 	Assuming no magnetic impurities and weak coupling, his expressions reduce to

### 2020-08-11 paper.tex
Add beginning of section 3

@@
 	\begin{equation}
-		\epsilon(q, \omega) = 1 + \frac{3 \pi}{\omega^2} \frac{n e^2}{m} \left[\int_{\Delta - \omega}^{\Delta}\dd{\omega'} \tanh(\frac{\omega + \omega'}{2 T}) I_1 + \int_{\Delta}^{\infty} \dd{\omega'} \left( \tanh(\frac{\omega + \omega'}{2 T}) I_1  - \tanh(\frac{\omega'}{2 T})I_2 \right) \right],
+		\epsilon(q, \omega) = 1 + \frac{3 \pi}{\omega^2} \frac{n e^2}{m} \left[\int_{\Delta - \omega}^{\Delta}\dd{\omega'} \tanh(\frac{\omega + \omega'}{2 T}) I_1 + \int_{\Delta}^{\infty} \dd{\omega'} \left( \tanh(\frac{\omega + \omega'}{2 T}) I_1  - \tanh(\frac{\omega'}{2 T})I_2 \right) \right], \label{eq:eps}
 	\end{equation}
@@
 
-	Nam's expressions are no longer valid for $k \geq k_\mathrm{F}$, and as $k \rightarrow \infty$ exhibit an unphysical $\flatfrac{1}{k}$ dependence.
-	In order to use~\eqref{eq:zp} and~\eqref{eq:zs}
+	Nam's expressions are no longer valid for $k \geq k_\mathrm{F}$, and as $k \rightarrow \infty$ exhibit an unphysical $\flatfrac{1}{k}$ dependence, a feature shared by similar expressions in \cite{AGD}.
+	In order to use~\eqref{eq:zp} and~\eqref{eq:zs}, this must be corrected to prevent divergences.
+	For sufficiently large momenta, the response function should approach the normal state function\todo{add good ref of this}.
+	Moreover, $\Im \epsilon$ should go to $0$ when $k \gtrapprox 2 \vf$, as otherwise there will be no available states within the Fermi surface for energy transfer (for more on this point, see the discussion in~\cite{FetterWalecka}).
+
+	In order to account for the first point, for the normal state we can use the Lindahrd dielectric function, which has the correct nonlocal behaviour to describe the low $z$ noise\cite{QubitRelax}.
+	The
+
 \begin{itemize}
-	\item Limitations on superconducting dielectric function.
-	In every expression that's worked out for arbitrary momentum, the large-momentum dependence goes as $\frac{1}{k}$, which is clearly unphysical.
-	Issue exists in~\cite{Nam1967, AGD, Tinkham}, etc.
 	\item Include description of cutoff process.
-	\item Include description of the interpolation process.
 	\item Is the numerics of picking the relevant unit scales / discussion of convergence interesting?

### 2020-08-11 paper.tex
add note about numerical inaccuracies

@@
 
-	Nam's expressions are no longer valid for $k \geq k_\mathrm{F}$, and as $k \rightarrow \infty$ exhibit an unphysical $\flatfrac{1}{k}$ dependence, a feature shared by similar expressions in \cite{AGD}.
+	Nam's expressions are no longer valid for $q \geq q_\mathrm{F}$, and as $q \rightarrow \infty$ exhibit an unphysical $\flatfrac{1}{q}$ dependence, a feature shared by similar expressions in \cite{AGD}.
 	In order to use~\eqref{eq:zp} and~\eqref{eq:zs}, this must be corrected to prevent divergences.
 	For sufficiently large momenta, the response function should approach the normal state function\todo{add good ref of this}.
-	Moreover, $\Im \epsilon$ should go to $0$ when $k \gtrapprox 2 \vf$, as otherwise there will be no available states within the Fermi surface for energy transfer (for more on this point, see the discussion in~\cite{FetterWalecka}).
+	Moreover, $\Im \epsilon$ should go to $0$ when $q \gtrapprox 2 k_{\mathrm{F}}$, as otherwise there will be no available states within the Fermi surface for energy transfer (for more on this point, see the discussion in~\cite{FetterWalecka}).
 
-	In order to account for the first point, for the normal state we can use the Lindahrd dielectric function, which has the correct nonlocal behaviour to describe the low $z$ noise\cite{QubitRelax}.
-	The
+	In order to account for the first point, for the normal state we can use the Lindhard dielectric function, which has the correct nonlocal behaviour to describe the low $z$ noise\cite{QubitRelax}.
+	As described from~\cite{SolyomV3}, this is
+	\begin{equation}
+		\epsilon_{\mathrm{Lindhard}}(\vec{q}, \omega) = 1 + \frac{q_{TF}^2}{q^2}\frac{\displaystyle 1 + \frac{\omega + \flatfrac{i}{\tau}}{2 \vf q} \ln(\frac{\omega - \vf q + \flatfrac{i}{\tau}}{\omega + \vf q + \flatfrac{i}{\tau}})}{\displaystyle 1 + \frac{\flatfrac{i}{\tau}}{2 \vf q} \ln(\frac{\omega - \vf q + \flatfrac{i}{\tau}}{\omega + \vf q + \flatfrac{i}{\tau}})}.
+\label{eq:lindhardsolyom}
+	\end{equation}
 
-\begin{itemize}
-	\item Include description of cutoff process.
-	\item Is the numerics of picking the relevant unit scales / discussion of convergence interesting?
-	It might be too obvious that the convergence is expected because these are real quantities.
-	\item Any other potentially interesting approximations?
-	Some integrals have regions entirely discarded because they are too small to matter, which is why the expressions in the Mathematica package are much simpler than what's in Nam.
-\end{itemize}
+	The effect of the inaccurate large momentum values in $\epsilon$ is an overestimation of the dissipative part $\Im r_p$ of the reflection coefficient.
+	To correct for this, we can use~\eqref{eq:lindhardsolyom} and~\eqref{eq:eps} to find $r_{p\mathrm{, Lindhard}}$ and $r_{p\mathrm{, Nam}}$, then choose whichever value has a smaller imaginary part.
+	Effectively, this defines an $r_{p\mathrm{, effective}}$.
+	For $q$ below some cutoff $q_{uc}$ on the order of $q_{\mathrm{F}}$, this picks the Nam reflection coefficient and reflects the diminished noise in the superconducting state.
+
+	The integral in~\eqref{eq:chi} picks out values around $u = \frac{c}{\omega} q \sim \frac{1}{z}$.
+	As long as $\frac{1}{z} \ll \frac{\omega}{c} q_{uc}$, the value for the noise will reflect the effects of the superconducting expressions, without picking up the inaccuracies of the transition region.
 

### 2020-08-11 paper.tex
add a todo

@@
 	Effectively, this defines an $r_{p\mathrm{, effective}}$.
-	For $q$ below some cutoff $q_{uc}$ on the order of $q_{\mathrm{F}}$, this picks the Nam reflection coefficient and reflects the diminished noise in the superconducting state.
+	For $q$ below some cutoff $q_{uc}$ on the order of $q_{\mathrm{F}}$, this picks the Nam reflection coefficient and reflects the diminished noise in the superconducting state.\todo{Does this need to be justified with a graph of the results?}
 

### 2020-08-11 paper.tex
fix wording

--- 2020-08-11 paper.tex
@@
 	Effectively, this defines an $r_{p\mathrm{, effective}}$.
-	For $q$ below some cutoff $q_{uc}$ on the order of $q_{\mathrm{F}}$, this picks the Nam reflection coefficient and reflects the diminished noise in the superconducting state.
+	For $q$ below some cutoff $q_{uc}$ on the order of $q_{\mathrm{F}}$, this picks the Nam reflection coefficient and reflects the diminished noise in the superconducting state.\todo{Does this need to be justified with a graph of the two functions?}
 

### 2020-08-25 paper.tex
changing whitespace problems
Adding precise z lower limit
revamps method section

@@
 
-	The relaxation rate for an electric qubit with dipole moment $\vec{d}$ a distance $r$ from a half space, described in~\cite{Henkel1999} and~\cite{QubitRelax}, can be written\todo{Add description here of how and why (e.g.
-Fermi's golden rule + FD theorem)}
+The electromagnetic field fluctuations that contribute to qubit relaxation haven described in~\cite{QubitRelax} and~\cite{Henkel1999}.
+Both use Fermi's golden rule and the fluctuation-dissipation theorem to relate the relaxation rate to the spectral density of the field fluctations:
 \begin{equation}
-		\frac{1}{T_1} = \frac{d^2}{\hbar \epsilon_0} \frac{\omega^3}{c^3} \chi_{i}^{E}(r, \omega) \coth\frac{\omega}{2 T}.
+	\frac{1}{T_1} = \frac{d_{(E,B)}^2}{\epsilon_0} \frac{\omega^3}{c^3} \chi_{i}^{(E,B)}(r, \omega) \coth\frac{\omega}{2 T}.
 \end{equation}
-	For a qubit pointing perpendicular to the surface of the half space,
+Here, $\vec{d}_{(E,B)}$ is the dipole moment of a point qubit at position $\vec{r}$, with $i$ the direction of the qubit's dipole moment, with $(E,B)$ represents an electric or magnetic qubit (and correspondingly, an electric or magnetic spectral field density).
+The frequency $\omega$ corresponds to the separation between energy levels of the qubit, and here and elsewhere we take $\hbar = k_{\mathrm{B}} = 1$.
+
+For a half space, these spectral densities can be written in terms of the surface's reflection coefficients, as derived by\cite{Henkel1999}.
+Considering for now a qubit pointing in the direction perpendicular to the half-space, we can write
 \begin{align}
-		\chi_\perp^E(z, \omega) &= \Re \int_0^{+\infty} \dd{u} \frac{u^3}{v} e^{2 i z v} r_p(u). \label{eq:chi}
+	\chi_\perp^E(z, \omega) &= \Re \int_0^{+\infty} \dd{u} \frac{u^3}{v} e^{2 i z v} r_p(u), \label{eq:chi}
 \end{align}
-	Here, $z$ is measured in units of the vacuum wavelength $\frac{c}{\omega}$, $v = \sqrt{1 - u^2}$ and we take the root $v = i \sqrt{u^2 - 1}$ for $u \geq 1$.
+with $z$ the distance to the qubit from the half-space measured in terms of the vacuum wavelength $\lambda = \flatfrac{c}{\omega}$.
+The integration variable $u$ effectively represents a momentum in units of $\flatfrac{1}{\lambda}$, with $v = \sqrt{1 - u^2}$.
+If $v \geq 1$, we take the positive square root $v = i \sqrt{u^2 - 1}$.
+The magnetic spectral density is the same, except with an additional factor of $\flatfrac{1}{c^2}$ and with $r_s$ instead of $r_p$.
 
-	The reflection coefficients are described by Ford and Weber~\cite{Ford1984}\todo{Add description of conditions and derivation methods, surface impedance are in quasistatic limit}:
+For the description of the behaviour of~\eqref{eq:chi} to remain accurate for small $z$, we use the reflection coefficients in Ford and Weber~\cite{Ford1984}:
 \begin{align}
@@
 \end{align}
-	As noted in~\cite{QubitRelax}, these expressions remain valid even for nonlocal descriptions of the dielectric constant.
+The treatment in~\cite{QubitRelax} compares the difference between these expressions and the simpler Fresnel reflection coefficients.
+In effect, using the Fresnel reflection coefficients for a metal for some constant conductivity corresponds to a local limit $u \rightarrow 0$.
 
-	Nam~\cite{Nam1967} describes the electrodynamics for superconductors applicable for clean and dirty materials.\todo{Describe his derivations here, based on Green's function methods \& can generalise to strong-coupling and magnetic impurities}
-	Assuming no magnetic impurities and weak coupling, his expressions reduce to
+The dielectric function $\epsilon(q, \omega)$, then, contains the information needed to describe the electromagnetic properties of the surface near the qubit.
+For the normal state, the dielectric function derived by Lindhard~\cite{Lindhard} used in~\cite{QubitRelax} describes the non-local electromagnetic response of a metal.
+Using the form described by Solyom\cite{SolyomV3},
+\begin{equation}
+	\epsilon_{\mathrm{Lindhard}}(\vec{q}, \omega) = 1 + \frac{q_{TF}^2}{q^2}\frac{\displaystyle 1 + \frac{\omega + \flatfrac{i}{\tau}}{2 \vf q} \ln(\frac{\omega - \vf q + \flatfrac{i}{\tau}}{\omega + \vf q + \flatfrac{i}{\tau}})}{\displaystyle 1 + \frac{\flatfrac{i}{\tau}}{2 \vf q} \ln(\frac{\omega - \vf q + \flatfrac{i}{\tau}}{\omega + \vf q + \flatfrac{i}{\tau}})}.
+\label{eq:lindhardsolyom}
+\end{equation}
+Here, $q_{TF}$ is the Thomas-Fermi wavevector $q_{TF}^2 = 3 \flatfrac{\omega_p^2}{\vf^2}$, $\omega_p$ is the plasma frequency $\sqrt{\flatfrac{4 \pi n e^2}{m}}$, $\tau$ is the collision time and $\vf$ is the Fermi velocity.
+This can be shown to reduce to the Drude dielectric function in the $q \rightarrow 0$ limit.
+
+We use the expressions from Nam in~\cite{Nam1967} to represent the superconducting response function.
+This extends the previous models by Mattis and Bardeen~\cite{Mattis} and Abrikosov, Dzyaloshinskii and Gorkov\cite{AGD} to give expressions that allow for broader ranges of impurity values.\todo{Including the full expressions from Nam here is a bit space-prohibitive, but it may be important to show exactly what our assumptions encode to in his notation?
+ex: by assuming no magnetic impurities, our renormalisation factor becomes simpler.}
+
+Here, we look at Nam's expressions in the weak coupling limit, for no magnetic impurities and an isotropic material.
 \begin{equation}
@@
 \end{align}
-
-	As seen in figure\todo{Insert 3D plot here}, the temperature dependence for the superconducting state is richer than for the normal state described in~\cite{QubitRelax}.
-	When $\omega$ and $T$ are both much smaller than $T_c$, the figure reveals the expected reduction in noise.
-	As $T \rightarrow T_c$, a smaller $\omega$ is required to facilitate Johnson noise.
-	In figure\todo{Insert chi vs T plot, for Lindhard and Nam}, the more sensitive temperature dependence of the superconductor is visible against a normal state calculation done with the Lindhard function, as in~\cite{QubitRelax}.
-	For $T \rightarrow T_c$, the superconducting state noise approaches that of the normal state, as expected.
+The assumption of isotropy suppresses the $q$ dependence for $\Delta$, which then is just a function of temperature, and can be described using the well-known BCS expression $\Delta \approx 3.06 \sqrt{T_c(T_c - T)}$ (see for example \cite{Tinkham}).
 
@@
 	Moreover, $\Im \epsilon$ should go to $0$ when $q \gtrapprox 2 k_{\mathrm{F}}$, as otherwise there will be no available states within the Fermi surface for energy transfer (for more on this point, see the discussion in~\cite{FetterWalecka}).
-
 	In order to account for the first point, for the normal state we can use the Lindhard dielectric function, which has the correct nonlocal behaviour to describe the low $z$ noise\cite{QubitRelax}.
-	As described from~\cite{SolyomV3}, this is
-	\begin{equation}
-		\epsilon_{\mathrm{Lindhard}}(\vec{q}, \omega) = 1 + \frac{q_{TF}^2}{q^2}\frac{\displaystyle 1 + \frac{\omega + \flatfrac{i}{\tau}}{2 \vf q} \ln(\frac{\omega - \vf q + \flatfrac{i}{\tau}}{\omega + \vf q + \flatfrac{i}{\tau}})}{\displaystyle 1 + \frac{\flatfrac{i}{\tau}}{2 \vf q} \ln(\frac{\omega - \vf q + \flatfrac{i}{\tau}}{\omega + \vf q + \flatfrac{i}{\tau}})}.
-\label{eq:lindhardsolyom}
-	\end{equation}
 
@@
 	As long as $\frac{1}{z} \ll \frac{\omega}{c} q_{uc}$, the value for the noise will reflect the effects of the superconducting expressions, without picking up the inaccuracies of the transition region.
+	This corresponds with physical distances on the order of $\SI{1}{\nm}$ for metals with $\vf \sim \SI{1e6}{\m\per\s}$.
+	For $z$ smaller than this, more sophisticated dielectric functions would be necessary to take into account inter-atomic spacing.
 

### 2020-09-11 paper.tex
beginning section 3

@@
 \begin{equation}
-	\epsilon(q, \omega) = 1 + \frac{3 \pi}{\omega^2} \frac{n e^2}{m} \left[\int_{\Delta - \omega}^{\Delta}\dd{\omega'} \tanh(\frac{\omega + \omega'}{2 T}) I_1 + \int_{\Delta}^{\infty} \dd{\omega'} \left( \tanh(\frac{\omega + \omega'}{2 T}) I_1  - \tanh(\frac{\omega'}{2 T})I_2 \right) \right], \label{eq:eps}
+	\epsilon_{\mathrm{Nam}}(\vec{q}, \omega) = 1 + \frac{3 \pi}{\omega^2} \frac{n e^2}{m} \left[\int_{\Delta - \omega}^{\Delta}\dd{\omega'} \tanh(\frac{\omega + \omega'}{2 T}) I_1 + \int_{\Delta}^{\infty} \dd{\omega'} \left( \tanh(\frac{\omega + \omega'}{2 T}) I_1  - \tanh(\frac{\omega'}{2 T})I_2 \right) \right], \label{eq:eps}
 \end{equation}
@@
 	&\quad + F(q, \Re[\sqrt{(\omega +  \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}]) (g - 1) \\
-	F(q, E) &= \frac{1}{q \vf} \left[2 S(E) + (1 - S(E)^2)\ln(\frac{S(E) + 1}{S(E) - 1})\right]  \\
+	F(q, E) &= \frac{1}{q \vf} \left[2 S(E) + (1 - S(E)^2)\ln(\frac{S(E) + 1}{S(E) - 1})\right] \label{eq:NamF} \\
 	S(q, E) &= \frac{1}{q \vf} \left( E - i \left(\Im[\sqrt{(\omega + \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}] + \frac{2}{\tau} \right) \right) \\
@@
 
-	Nam's expressions are no longer valid for $q \geq q_\mathrm{F}$, and as $q \rightarrow \infty$ exhibit an unphysical $\flatfrac{1}{q}$ dependence, a feature shared by similar expressions in \cite{AGD}.
-	In order to use~\eqref{eq:zp} and~\eqref{eq:zs}, this must be corrected to prevent divergences.
-	For sufficiently large momenta, the response function should approach the normal state function\todo{add good ref of this}.
-	Moreover, $\Im \epsilon$ should go to $0$ when $q \gtrapprox 2 k_{\mathrm{F}}$, as otherwise there will be no available states within the Fermi surface for energy transfer (for more on this point, see the discussion in~\cite{FetterWalecka}).
-	In order to account for the first point, for the normal state we can use the Lindhard dielectric function, which has the correct nonlocal behaviour to describe the low $z$ noise\cite{QubitRelax}.
+The noise integral \eqref{eq:chi} can be calculated numerically, with proper care taken to handle the integrand's behaviour across the entire range.
+For small momenta, where $\vf q \ll \omega$, both \eqref{eq:lindhardsolyom} and \eqref{eq:eps} can be series expanded to give explicit expressions.
+The Lindhard dielectric function, up to $\mathcal{O}(q^2)$, becomes
+\begin{gather}
+	\epsilon_{\mathrm{Lindhard}}(\vec{q}, \omega) = 1 - \frac{\omega_p^2}{\omega^2} \left(\frac{\omega}{(\omega + \frac{i}{\tau})} + (\vf q)^2  \frac{9 \omega + 5 \frac{i}{\tau}}{15 (\omega + \frac{i}{\tau})^3} \right).
+\label{eq:lindhardsmallkseries}
+\end{gather}
+As expected for a description of the normal state, for $q \rightarrow 0$ this reduces to the Drude expression.
 
-	The effect of the inaccurate large momentum values in $\epsilon$ is an overestimation of the dissipative part $\Im r_p$ of the reflection coefficient.
-	To correct for this, we can use~\eqref{eq:lindhardsolyom} and~\eqref{eq:eps} to find $r_{p\mathrm{, Lindhard}}$ and $r_{p\mathrm{, Nam}}$, then choose whichever value has a smaller imaginary part.
-	Effectively, this defines an $r_{p\mathrm{, effective}}$.
-	For $q$ below some cutoff $q_{uc}$ on the order of $q_{\mathrm{F}}$, this picks the Nam reflection coefficient and reflects the diminished noise in the superconducting state.\todo{Does this need to be justified with a graph of the two functions?}
+All of the momentum dependence in the Nam expression is contained within the $F(q, E)$ function in \eqref{eq:NamF}.
+Expanding this out to second order in the momentum gives
+\begin{align}
+	F = \frac43 \frac{1}{\eta} + (\vf q)^2\frac{4}{15} \frac{1}{\eta^3},
+\end{align}
+where
+\begin{equation}
+	\eta = E - i \left(\Im[\sqrt{(\omega + \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}] + 2 \frac{1}{\tau} \right).
+\end{equation}
+This, and other limiting forms, were stated by Nam as well~\cite{Nam1967}.
+Inserting this in $\eqref{eq:NamF}$ suffices to obtain the small $q$ values in a more numerically stable way.
 
-	The integral in~\eqref{eq:chi} picks out values around $u = \frac{c}{\omega} q \sim \frac{1}{z}$.
-	As long as $\frac{1}{z} \ll \frac{\omega}{c} q_{uc}$, the value for the noise will reflect the effects of the superconducting expressions, without picking up the inaccuracies of the transition region.
-	This corresponds with physical distances on the order of $\SI{1}{\nm}$ for metals with $\vf \sim \SI{1e6}{\m\per\s}$.
-	For $z$ smaller than this, more sophisticated dielectric functions would be necessary to take into account inter-atomic spacing.
+By comparison to the $q \rightarrow 0$ case, the large momentum dependence requires more careful thought.
+For sufficiently large $q$, the logarithm in $\eqref{eq:NamF}$ goes to $i \pi$, and $F \rightarrow \frac{i \pi}{q \vf}$.
+This behaviour leads to an unphysical divergence in \eqref{eq:chi}, as
 

### 2020-09-11 paper.tex
Adds large k description to section 3

@@
 
-By comparison to the $q \rightarrow 0$ case, the large momentum dependence requires more careful thought.
+By comparison to the $q \rightarrow 0$ case, the large momentum dependence is more involved to correctly handle.
 For sufficiently large $q$, the logarithm in $\eqref{eq:NamF}$ goes to $i \pi$, and $F \rightarrow \frac{i \pi}{q \vf}$.
-This behaviour leads to an unphysical divergence in \eqref{eq:chi}, as
+This behaviour leads to an unphysical divergence in \eqref{eq:chi} as $z \rightarrow 0$.
+Tinkham~\cite{Tinkham} and Abrikosov, Dzyaloshinskii and Gorkov~\cite{AGD} both describe expressions with this same $\frac{1}{q}$ dependence.
+The root cause of inaccuracies above $q \gg 2 q_{\mathrm{F}}$ is that the Green's function method used to derive the superconducting response function makes the assumption that $q$ is sufficiently close to the Fermi surface.
+
+However, it is insufficient to only account for the $\frac{1}{q}$ dependence, as a stronger condition is necessary to ensure convergence for arbitrarily small $z$.
+In the large $q$ regime, \eqref{eq:chi} can be reduced to
+\begin{align}
+	\chi_\perp^E(z, \omega) &= \Re \int_0^{+\infty} \dd{u} \frac{u^3}{i u} e^{-2 z u} r_p(u),
+\end{align}
+which means that for $z = 0$
+\begin{align}
+	\chi_\perp^E(z, \omega) &= \int_0^{+\infty} \dd{u} u^2 \Im r_p(u).
+\end{align}
+For a dielectric function that asymptotically scales as $\frac{A + i B}{q}$, for real $A$ and $B$, it can be shown that
+\begin{equation}
+	\Im r_p(u) \sim \frac{B}{u},
+\end{equation}
+which clearly leads to a divergent $\chi_\perp^E$.
+
+This is the same divergence discussed in Langsjoen et al.~\cite{QubitRelax}, where for the normal state this problem does not arise if the Lindhard dielectric function is used.
+Ultimately, this is because for $q > 2 q_{\mathrm{F}}$ the imaginary part of the Lindhard function goes to zero.
+Physically, this happens because there are no points on the assumed spherical Fermi surface further than $2 q_{\mathrm{F}}$ apart, which means there are no available quasiparticle-hole excitations available for energy dissipation (cf discussion in \cite{AGD}, \cite{FetterWalecka} or \cite{SolyomV3}).
+This is a general argument, and it should be expected that a superconducting dielectric function should also have zero imaginary part above some momentum on the order of the Fermi momentum.
+
+This can be handled in two coarse approximations.
+The key is that the integral in \eqref{eq:chi} picks out values around $u = \frac{c}{\omega} \sim \frac{1}{z}$ over most of its range, because of the $u^2 e^{-2 z u}$ factor for $u \gg 1$.
+If we cut off the imaginary part of the Nam response function above some momentum $q_{\mathrm{cutoff}}$, then if $\frac{1}{z} \ll \frac{\omega}{c} q_{\mathrm{cutoff}}$, the imprecision of such a low order approximation will not greatly affect the final noise integral.
+For a metal with $\vf \sim \SI{e6}{\m\per\s}$, this corresponds to $z \sim \SI{1}{\nm}$.
+At this length scale, inter-atomic spacing would itself be enough to invalidate these results already.
+
+As a further correction, the Nam expression's $\frac{1}{q}$ dependence causes an overestimation in $\chi_\perp^E$ if $\frac{1}{z}$ is above the momentum at which superconductivity should play a role, on the order of the Debye momentum.
+Above this point, the Lindhard result suffices as a description of the metal's response.
+This can be incorporated into a numerical model by interpolating the results;
+one crude way of accomplishing this is to simply define a new effective reflection coefficient
+\begin{equation}
+	r_{p, \mathrm{effective}}(u) = \min_{\Im}\left[r_{p, \mathrm{Lindhard}}\left(u\right), r_{p, \mathrm{Nam}}\left(u\right)\right],
+\end{equation}
+where the right hand side should be interpreted to choose the argument with the smaller imaginary part.
+This effectively forces the reflection coefficient to choose the Lindhard result above some crossover $q_{\mathrm{crossover}}$.
+Once again, unless $\frac{1}{z} \sim q_{\mathrm{crossover}}$, the inaccuracies this causes should be exponentially damped in $\chi_\perp^E$.
 

### 2021-01-26 paper.tex
adds title
Additional description of the nonlocal case vs local

@@
 
-\title{Title}
+\title{EWJN from a BCS Superconductor}
 
@@
 
-The electromagnetic field fluctuations that contribute to qubit relaxation haven described in~\cite{QubitRelax} and~\cite{Henkel1999}.
-Both use Fermi's golden rule and the fluctuation-dissipation theorem to relate the relaxation rate to the spectral density of the field fluctations:
+Physically, we are interested in the relaxation time of a qubit near the surface of the metal.
+Sufficiently close to the metal, such that the separation between qubit and metal is much smaller than the shortest dimension of the metallic body, we can approximate the metal as a half space.
+This defines a natural coordinate system, and we can allow the metal to take up all points with $z$-coordinate less than zero, extending to infinity in the $x$ and $y$ directions.
+
+For a charge qubit with level separation $\omega$ and dipole moment $\vec{d}$, the relaxation rate $\frac{1}{T_1}$ depends on the qubit's distance from the surface $z$, as well as its orientation $i$.
+The vacuum wavelength $\lambda = \frac{c}{\omega}$ is a natural unit for this distance $z$, so we wil measure $z$ in units of $\lambda$.
+The electromagnetic field fluctuations that contribute to qubit relaxation have been described in~\cite{QubitRelax} and~\cite{Henkel1999}.
+Both use Fermi's golden rule and the fluctuation-dissipation theorem to relate the relaxation rate to the spectral density of the field fluctations, and obtain the following expression:
 \begin{equation}
-	\frac{1}{T_1} = \frac{d_{(E,B)}^2}{\epsilon_0} \frac{\omega^3}{c^3} \chi_{i}^{(E,B)}(r, \omega) \coth\frac{\omega}{2 T}.
+	\frac{1}{T_1} = \frac{d^2}{\epsilon_0} \frac{\omega^3}{c^3} \chi_{i}^{(E)}(z, \omega) \coth\frac{\omega}{2 T}.
 \end{equation}
-Here, $\vec{d}_{(E,B)}$ is the dipole moment of a point qubit at position $\vec{r}$, with $i$ the direction of the qubit's dipole moment, with $(E,B)$ represents an electric or magnetic qubit (and correspondingly, an electric or magnetic spectral field density).
-The frequency $\omega$ corresponds to the separation between energy levels of the qubit, and here and elsewhere we take $\hbar = k_{\mathrm{B}} = 1$.
+\todo{All the Nam stuff is in Gaussian units, so should pick one unit system and stick with it.
+Doesn't affect results so far, as \chi is unitless and only depends on quantities that are the same in SI / Gaussian.
+Still bad though.}
+Here and elsewhere we take $\hbar = k_{\mathrm{B}} = 1$.
 
-For a half space, these spectral densities can be written in terms of the surface's reflection coefficients, as derived by\cite{Henkel1999}.
+Similarly, for spin qubits with dipole moment $\vec{\mu}$, both~\cite{QubitRelax} and~\cite{Henkel1999} have a similar expression with a different spectral density expression:
+\begin{equation}
+	\frac{1}{T_1} = \frac{\mu^2}{\epsilon_0} \frac{\omega^3}{c^3} \chi_{i}^{(B)}(z, \omega) \coth\frac{\omega}{2 T}.
+\end{equation}
+
+The spectral densities are in general functions of the geometry and electrodynamic response of the metal object.
+A standard limiting case for the response is that of local, linear electrodynamics, where the relationship between the electric displacement $\vec{D}$ and electric field $\vec{E}$ is a proportionality:
+\begin{equation}
+	\vec{D}(\vec{r}) = \epsilon \vec{E}(\vec{r})
+\end{equation}
+For a metal with conductivity $\sigma$, this dielectric function will typically have a large imaginary value as determined by the Drude expression in Gaussian units:
+\begin{equation}
+	\epsilon = 1 + i\frac{4 \pi \sigma}{\omega}
+\end{equation}
+
+For a half space, these spectral densities can be written in terms of the surface's reflection coefficients, as derived by\cite{Henkel1999} for local electrodynamics.
 Considering for now a qubit pointing in the direction perpendicular to the half-space, we can write
 \begin{align}
-	\chi_\perp^E(z, \omega) &= \Re \int_0^{+\infty} \dd{u} \frac{u^3}{v} e^{2 i z v} r_p(u), \label{eq:chi}
+	\chi_\perp^E(z, \omega) &= \Re \int_0^{+\infty} \dd{u} \frac{u^3}{v} e^{2 i z v} r_p(u). \label{eq:chi}
 \end{align}
-with $z$ the distance to the qubit from the half-space measured in terms of the vacuum wavelength $\lambda = \flatfrac{c}{\omega}$.
 The integration variable $u$ effectively represents a momentum in units of $\flatfrac{1}{\lambda}$, with $v = \sqrt{1 - u^2}$.
@@
 The magnetic spectral density is the same, except with an additional factor of $\flatfrac{1}{c^2}$ and with $r_s$ instead of $r_p$.
+In the local limit, for dielectric constant $\epsilon$, the reflection coefficients will be the Fresnel $r_p$ and $r_s$:
+\begin{align}
+	r_p &= \frac{\epsilon v - \sqrt{\epsilon - u^2}}{\epsilon v + \sqrt{\epsilon - u^2}} \\
+	r_s &= \frac{v - \sqrt{\epsilon - u^2}}{ v + \sqrt{\epsilon - u^2}}
+\end{align}
 
-For the description of the behaviour of~\eqref{eq:chi} to remain accurate for small $z$, we use the reflection coefficients in Ford and Weber~\cite{Ford1984}:
+However, as discussed in~\cite{QubitRelax} and~\cite{Henkel2006}, this expression no longer remains accurate for arbitrarily small distances, diverging as $\frac{1}{z^3}$ as $z \rightarrow 0$.
+The divergence here stems from the unphysicality of local electrodynamics at very small scales;
+within the electromagnetic coherence length of the metal the full response function defined by
+\begin{equation}
+	\vec{D}(\vec{r, t}) = \int \dd{r'} \dd{t'} \epsilon(r, r', t, t') \vec{E}(\vec{r', t'})
+\end{equation}
+becomes necessary.
+
+We can keep~\eqref{eq:chi} accurate for sufficiently small $z$ if we make appropriate changes to our reflection coefficients\cite{QubitRelax,Henkel2006}, so 
+we use the reflection coefficients in Ford and Weber~\cite{Ford1984}:
 \begin{align}

### 2021-01-29 paper.tex
Adds more text about the cutoff and lack of cutoff in Lindhard case

@@
 
-However, as discussed in~\cite{QubitRelax} and~\cite{Henkel2006}, this expression no longer remains accurate for arbitrarily small distances, diverging as $\frac{1}{z^3}$ as $z \rightarrow 0$.
+However, as discussed in~\cite{QubitRelax} and~\cite{Henkel2006}, this expression no longer remains accurate for arbitrarily small distances, with \eqref{eq:chi} diverging as $\frac{1}{z^3}$ as $z \rightarrow 0$.
 The divergence here stems from the unphysicality of local electrodynamics at very small scales;
-within the electromagnetic coherence length of the metal the full response function defined by
+for $z$ smaller than the electromagnetic coherence length of the metal the full response function defined by
 \begin{equation}
@@
 becomes necessary.
+The experiment described by Kolkowitz et al.\cite{Kolkowitz2015} gives an example of a physical situation where the local description is insufficient, with a qubit probe at a distance from a silver film less than the film's mean free path.
+Given that the coherence lengths of typical BCS superconductors can be larger than the distances used in that experiment, we should expect that the purely local description will not work for the superconducting case.
 
-We can keep~\eqref{eq:chi} accurate for sufficiently small $z$ if we make appropriate changes to our reflection coefficients\cite{QubitRelax,Henkel2006}, so 
-we use the reflection coefficients in Ford and Weber~\cite{Ford1984}:
+We can keep~\eqref{eq:chi} accurate for sufficiently small $z$ if we make appropriate changes to our reflection coefficients\cite{QubitRelax,Henkel2006}, so we use the reflection coefficients in Ford and Weber~\cite{Ford1984}:
 \begin{align}
@@
 \end{align}
+The quantities $\zeta_p$ and $\zeta_s$ are proportional to the surface impedances of the metal, derived for this case by Ford and Weber\cite{Ford1984}, and with more thorough discussion in~\cite{LandauLifshitzElectrodynamics}.
 The treatment in~\cite{QubitRelax} compares the difference between these expressions and the simpler Fresnel reflection coefficients.
-In effect, using the Fresnel reflection coefficients for a metal for some constant conductivity corresponds to a local limit $u \rightarrow 0$.
 
@@
 This can be shown to reduce to the Drude dielectric function in the $q \rightarrow 0$ limit.
+
+The Lindhard dielectric function reflects the important property of having an imaginary part that vanishes for $q$ such that $\abs{\varepsilon_q - \omega} >  q\vf$.
+This is a very generic feature of these types of response functions, and occurs because there are no points on the assumed spherical Fermi surface further than $2 q_{\mathrm{F}}$ apart.
+Thus, there are no available quasiparticle-hole excitations available for energy dissipation (cf discussion in \cite{AGD}, \cite{FetterWalecka} or \cite{SolyomV3}).
+This is a general argument, and it should be expected that a superconducting dielectric function should also have zero imaginary part above some momentum on the order of the Fermi momentum.
+Because the Lindhard dielectric function's imaginary part vanishes above a cutoff $q_c\left(\omega\right)$ and has real part that goes as $\frac{1}{q^2}$, all of the integrals in $\eqref{eq:chi}, \eqref{eq:zp} and \eqref{eq:zs}$ converge.
 
@@
 Ultimately, this is because for $q > 2 q_{\mathrm{F}}$ the imaginary part of the Lindhard function goes to zero.
-Physically, this happens because there are no points on the assumed spherical Fermi surface further than $2 q_{\mathrm{F}}$ apart, which means there are no available quasiparticle-hole excitations available for energy dissipation (cf discussion in \cite{AGD}, \cite{FetterWalecka} or \cite{SolyomV3}).
-This is a general argument, and it should be expected that a superconducting dielectric function should also have zero imaginary part above some momentum on the order of the Fermi momentum.
 

### 2021-02-02 paper.tex
Discussion from Meeting.

@@
 The electromagnetic field fluctuations that contribute to qubit relaxation have been described in~\cite{QubitRelax} and~\cite{Henkel1999}.
-Both use Fermi's golden rule and the fluctuation-dissipation theorem to relate the relaxation rate to the spectral density of the field fluctations, and obtain the following expression:
+Both use Fermi's golden rule and the fluctuation-dissipation theorem to relate the relaxation rate to the spectral density of the field fluctuations, and obtain the following expression:
 \begin{equation}
@@
 \end{equation}
-\todo{All the Nam stuff is in Gaussian units, so should pick one unit system and stick with it.
-Doesn't affect results so far, as \chi is unitless and only depends on quantities that are the same in SI / Gaussian.
+%\todo{All the Nam stuff is in Gaussian units, so should pick one unit system and stick with it.
+Doesn't %affect results so far, as $\chi$ is unitless and only depends on quantities that are the same in SI / %Gaussian.
 Still bad though.}
-Here and elsewhere we take $\hbar = k_{\mathrm{B}} = 1$.
+%Here and elsewhere we take $\hbar = k_{\mathrm{B}} = 1$.
 

### 2021-02-05 paper.tex
Adds logarithm branch cut
Adds figure calcs

--- 2021-01-29 paper.tex
@@
 Here, $q_{TF}$ is the Thomas-Fermi wavevector $q_{TF}^2 = 3 \flatfrac{\omega_p^2}{\vf^2}$, $\omega_p$ is the plasma frequency $\sqrt{\flatfrac{4 \pi n e^2}{m}}$, $\tau$ is the collision time and $\vf$ is the Fermi velocity.
+The branch cut for the logarithm is chosen here such that their imaginary parts lie between $\pm i \pi$.
 This can be shown to reduce to the Drude dielectric function in the $q \rightarrow 0$ limit.
@@
 This is a general argument, and it should be expected that a superconducting dielectric function should also have zero imaginary part above some momentum on the order of the Fermi momentum.
-Because the Lindhard dielectric function's imaginary part vanishes above a cutoff $q_c\left(\omega\right)$ and has real part that goes as $\frac{1}{q^2}$, all of the integrals in $\eqref{eq:chi}, \eqref{eq:zp} and \eqref{eq:zs}$ converge.
+Because the Lindhard dielectric function's imaginary part vanishes above a cutoff $q_c\left(\omega\right)$ and has real part that goes as $\Re \epsilon_{\mathrm{Lindhard}} - 1 \sim \frac{1}{q^2}$, all of the integrals in $\eqref{eq:chi}, \eqref{eq:zp} and \eqref{eq:zs}$ converge.
 

### 2021-02-05 paper.tex
Adds figures for the dielectric functions

@@
 
+\usepackage{cleveref}
+
 \title{EWJN from a BCS Superconductor}
@@
 \newcommand{\vf}{v_{\mathrm{F}}}
+\newcommand{\qf}{q_{\mathrm{F}}}
 
@@
 
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{Cond1Re}
+	\caption{$\Re[\epsilon(q)]$ for $\omega = 1$, $\tau = 0.5$, $\omega_p = 10$, $\vf = 1$, $T = .9999 T_c$, $T_c = 3$} \label{fig:cond1Re}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{Cond1Im}
+	\caption{$\Im[\epsilon(q)]$ for $\omega = 1$, $\tau = 0.5$, $\omega_p = 10$, $\vf = 1$, $T = .9999 T_c$, $T_c = 3$} \label{fig:cond1Im}
+\end{figure}
+
+The Lindhard and Nam dielectric constants are compared in \cref{fig:cond1Re} and \cref{fig:cond1Im}, plotting the real and imaginary part for small representative values.
+In this regime, $\omega_p > T_c > \omega$, as is typical for the frequency regime of interest, while $\tau$ is chosen to be smaller than $\omega$.
+For a typical metal in this description, the Fermi wavevector $\qf$ is around the same order as $\sqrt{3}\frac{\omega_p}{\vf}$ (see discussion on this point in Solyom\cite{SolyomV3}).
+We can see in \cref{fig:cond1Im} that the Lindhard dielectric function goes to zero for $q < \qf \approx 10 \sqrt{3}$.
+
 \section{Numerical Techniques \label{sec:technical}}

### 2021-02-05 paper.tex
Adds additional figures including cliffedge and scripts for nam and lindhard noise calculations

@@
 
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{HighTempNam1}
+	\caption{$T_1(z)$ at various temperatures, with $T_1$ in nanoseconds and $z$ in micrometers for parameters described in the text.} \label{fig:HighTempNam1}
+\end{figure}
+\Cref{fig:HighTempNam1} shows the result of these approximations, plotting the relaxation time $T_1$ at increasing distances away from the qubit.
+In that figure, $\omega = \SI{1e9}{\per\second}$, $\omega_p = \SI{3.5e15}{\per\second}$, $\tau = \SI{1e-14}{\second}$, $\vf = \SI{1e6}{\m\per\s}$, $T_c = \SI{1e11}{\per\s}$, $d = \SI{8.4e-30}{\coulomb\m}$, and the temperatures are given in the legend in units of $T_c$.
+Of note is how the noise calculated for the superconducting case goes to the normal state as $T \rightarrow T_c$, as well as how little the normal state depends on the temperature.
+Also of note is the very large increase in the relaxation time for $T = .9 T_c$.
+This reflects the situation where $\Delta$ is high enough that fluctuations with frequency $\omega$ can no longer excite states in the superconductor.
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{namNoiseCliff}
+	\caption{$\chi = \frac{1}{T_1(z)}$ for fixed $z$, but varying $\omega$ and $\Delta$} \label{fig:Cliff}
+\end{figure}
+This is plotted in \cref{fig:Cliff}, which shows the cliff-edge along which $\omega$ is sufficiently smaller than $\Delta$.
+In this regime, Johnson noise no longer becomes an issue for these qubits.
+
 \section{Experiments \label{sec:experiments}}

### 2021-02-14 paper.tex
Adds new details

@@
 
+\subsection{Qubit Relaxation Time Theory} \label{subsec:relaxtime}
 Physically, we are interested in the relaxation time of a qubit near the surface of the metal.
@@
 
+\subsubsection{Spectral Field Densities} \label{subsec:spectraldensities}
 The spectral densities are in general functions of the geometry and electrodynamic response of the metal object.
@@
 
+\subsubsection{Nonlocal Electrodynamics} \label{subsubsec:nonlocalelectrodynamics}
 However, as discussed in~\cite{QubitRelax} and~\cite{Henkel2006}, this expression no longer remains accurate for arbitrarily small distances, with \eqref{eq:chi} diverging as $\frac{1}{z^3}$ as $z \rightarrow 0$.
@@
 
-We can keep~\eqref{eq:chi} accurate for sufficiently small $z$ if we make appropriate changes to our reflection coefficients\cite{QubitRelax,Henkel2006}, so we use the reflection coefficients in Ford and Weber~\cite{Ford1984}:
+To keep~\eqref{eq:chi} accurate for sufficiently small $z$, appropriate changes to the reflection coefficients can be made\cite{QubitRelax,Henkel2006} through the reflection coefficients in Ford and Weber~\cite{Ford1984}:
 \begin{align}
@@
 
+\subsubsection{Normal state dielectric function} \label{subsubsec:lindharddielectric}
 The dielectric function $\epsilon(q, \omega)$, then, contains the information needed to describe the electromagnetic properties of the surface near the qubit.
@@
 
+\subsubsection{Superconducting dielectric function} \label{subsubsec:namdielectric}
 We use the expressions from Nam in~\cite{Nam1967} to represent the superconducting response function.
@@
 
-\section{Numerical Techniques \label{sec:technical}}
+\subsection{Numerical Techniques \label{subsec:technical}}
 

### 2021-02-14 paper.tex
Adds new structure

@@
 
+\subsubsection{Small momentum limit} \label{subsubsec:smallq}
 The noise integral \eqref{eq:chi} can be calculated numerically, with proper care taken to handle the integrand's behaviour across the entire range.
 For small momenta, where $\vf q \ll \omega$, both \eqref{eq:lindhardsolyom} and \eqref{eq:eps} can be series expanded to give explicit expressions.
-The Lindhard dielectric function, up to $\mathcal{O}(q^2)$, becomes
+Additionally, this small momentum limit is important in general as it tends towards the purely local limit.
+The Lindhard dielectric function, up to order $q^2$, becomes
 \begin{gather}
@@
 
-All of the momentum dependence in the Nam expression is contained within the $F(q, E)$ function in \eqref{eq:NamF}.
+For the superconducting case, all of the momentum dependence in the Nam expression is contained within the $F(q, E)$ function in \eqref{eq:NamF}.
 Expanding this out to second order in the momentum gives
@@
 
-By comparison to the $q \rightarrow 0$ case, the large momentum dependence is more involved to correctly handle.
+\subsubsection{Large momentum limit} \label{subsubsec:bigq}
+By comparison, the large momentum dependence is more involved to correctly handle.
+If we look at the portion of the integral in \eqref{eq:chi} for $u > u_l \gg 1$,
+\begin{align}
+	\chi_{\perp\ \mathrm{upper}}^E(z, \omega) &= \Re \int_{u_l}^{+\infty} \dd{u} \frac{u^3}{v} e^{2 i z v} r_p(u) \\
+	\chi_{\perp\ \mathrm{upper}}^E(z, \omega) &= \Re \int_{u_l}^{+\infty} \dd{u} \frac{u^3}{i u} e^{-2 z u} r_p(u)
+\end{align}
+which means that for $z = 0$
+\begin{align}
+	\chi_\perp^E(z, \omega) &= \int^{+\infty} \dd{u} u^2 \Im r_p(u).
+\end{align}
+In order for this to converge, $\Im r_p(u)$ must decrease faster than $\frac{1}{u^3}$
+
+This divergence is discussed for the normal state in Langsjoen et al.~\cite{QubitRelax}, where it only occurs in local electrodynamics.
+This is related to the point earlier that the imaginary part of $\epsilon$ should go to zero for $\abs{\varepsilon_q - \omega} > q \vf$, as such a condition is sufficient to ensure that $\Im r_p(u)$ decays quickly enough.
+
+\subsubsection{Superconducting large momentum limit} \label{subsubsec:scbigq}
+The superconducting case in the large momentum limit is not automatically corrected by using nonlocal expressions, however.
 For sufficiently large $q$, the logarithm in $\eqref{eq:NamF}$ goes to $i \pi$, and $F \rightarrow \frac{i \pi}{q \vf}$.
@@
 However, it is insufficient to only account for the $\frac{1}{q}$ dependence, as a stronger condition is necessary to ensure convergence for arbitrarily small $z$.
-In the large $q$ regime, \eqref{eq:chi} can be reduced to
-\begin{align}
-	\chi_\perp^E(z, \omega) &= \Re \int_0^{+\infty} \dd{u} \frac{u^3}{i u} e^{-2 z u} r_p(u),
-\end{align}
-which means that for $z = 0$
-\begin{align}
-	\chi_\perp^E(z, \omega) &= \int_0^{+\infty} \dd{u} u^2 \Im r_p(u).
-\end{align}
+
 For a dielectric function that asymptotically scales as $\frac{A + i B}{q}$, for real $A$ and $B$, it can be shown that
@@
 which clearly leads to a divergent $\chi_\perp^E$.
-
-This is the same divergence discussed in Langsjoen et al.~\cite{QubitRelax}, where for the normal state this problem does not arise if the Lindhard dielectric function is used.
-Ultimately, this is because for $q > 2 q_{\mathrm{F}}$ the imaginary part of the Lindhard function goes to zero.
 

### 2021-02-26 paper.tex
Adds figures to text

@@
 
+\section{Additional Figures}
+
+Slices of \cref{fig:Cliff} are plotted for different frequencies in \crefrange{fig:omega:5}{fig:omega:85}, to better show the behaviour of the cliff-edge.
+Additionally, we have plotted different values of the impurity collision frequency $\tau$, to show how dirtier superconductors, with smaller $\tau$, have much higher values for the noise.
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{constOmega/5.jpg}
+	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:5}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{constOmega/15.jpg}
+	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:15}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{constOmega/25.jpg}
+	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:25}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{constOmega/35.jpg}
+	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:35}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{constOmega/45.jpg}
+	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:45}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{constOmega/55.jpg}
+	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:55}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{constOmega/65.jpg}
+	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:65}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{constOmega/75.jpg}
+	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:75}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{constOmega/85.jpg}
+	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:85}
+\end{figure}
+
+Similarly, we can make slices of \cref{fig:Cliff} for constant temperature, and show how the noise drops off for a different frequency.
+These slices are plotted in \crefrange{fig:T:10}{fig:T:40}.
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{constT/10.jpg}
+	\caption{A slice of \cref{fig:Cliff} for constant $T$.} \label{fig:T:10}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{constT/20.jpg}
+	\caption{A slice of \cref{fig:Cliff} for constant $T$.} \label{fig:T:20}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{constT/30.jpg}
+	\caption{A slice of \cref{fig:Cliff} for constant $T$.} \label{fig:T:30}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=12cm]{constT/40.jpg}
+	\caption{A slice of \cref{fig:Cliff} for constant $T$.} \label{fig:T:40}
+\end{figure}
+
 \printbibliography
